Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-03-22 ProjectProposal.Rmd
Update source for weather

## Bayesian Framework for Estimation of Time-Varying R

@@

Here the parameter of interest is $\beta$ and the $\varepsilon_i(t)$ are nuisance variables. We propose to use Markov chain Monte Carlo to compute a joint distribution over all the parameters and marginalize over the $\varepsilon_i(t)$.
Because of concerns over confounding factors that may affect R and are correlated with temperature and humidity, we plan to add several other features to $x(t)$ to help control for these factors. We also need to restrict the analysis to the pre-lockdown regime in each province, because the lockdown is likely to change the magnitude of seasonal forcings.

@@

- The Italian government dataset at https://github.com/pcm-dpc/COVID-19 contains the disease incidence for each province. This data contains date of confirmation instead of date of onset of symptoms, and so some procedure may be necessary to correct for this. Abbott et al. (2020) outlines a technique to correct for reporting delays using an exponential distribution of reporting delay fit to line list data; we may use the same distribution.
- We also will need to find temperature and humidity data. We have located several possible sources and are evaluating them.

>>>>

## Bayesian Framework for Estimation of Time-Varying $R$

@@

Here the parameter of interest is $\beta$ and the $\varepsilon_i(t)$ are nuisance variables. We propose to use Markov chain Monte Carlo to compute a joint distribution over all the parameters and marginalize over the $\varepsilon_i(t)$.
Because of concerns over confounding factors that may affect $R$ and are correlated with temperature and humidity, we plan to add several other features to $x(t)$ to help control for these factors. We also need to restrict the analysis to the pre-lockdown regime in each province, because the lockdown is likely to change the magnitude of seasonal forcings.

@@

- The Italian government dataset at https://github.com/pcm-dpc/COVID-19 contains the disease incidence for each province. This data contains date of confirmation instead of date of onset of symptoms, and so some procedure may be necessary to correct for this. Abbott et al. (2020) outlines a technique to correct for reporting delays using an exponential distribution of reporting delay fit to line list data; we may use the same distribution.
- The `worldmet` R package enables access to temperature and humidity data, sourced from NOAA.
